---
title: "Ensemble forecasts with fable"
author: Rob J Hyndman
date: 14 August 2020
fontsize: 14pt
classoption: aspectratio=169
toc: false
output:
  binb::monash:
    fig_height: 4.33
    fig_width: 7
    colortheme: monashwhite
    keep_tex: yes
    includes:
      in_header: preamble.tex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  cache = TRUE,
  dev.args = list(bg = grey(0.9), pointsize = 11)
)
library(fpp3)
library(distributional)
library(gganimate)
set.seed(2020 - 08 - 10)

if (file.exists("cafe.rds")) {
  cafe <- readRDS("cafe.rds")
} else {
  cafe <- readabs::read_abs(series_id = "A3349870V") %>%
    select(date, value) %>%
    mutate(date = yearmonth(date)) %>%
    as_tsibble(index = date) %>%
    filter(
      date >= yearmonth("2006 Jan"),
      date <= yearmonth("2019 Dec")
    ) %>%
    rename(turnover = value)
  saveRDS(cafe, "cafe.rds")
}
```

```{r samples, echo=FALSE}
# Training data
train <- cafe %>%
  filter(year(date) <= 2018)
# Fit ETS model
fit <- train %>%
  model(ETS = ETS(turnover))
# Forecasts
fc <- fit %>%
  forecast(h = "1 year")
# Future sample paths
future <- fit %>%
  generate(times = 1000, h = "1 year") %>%
  as_tibble() %>%
  mutate(modrep = paste0(.model, .rep))
# Colours for sample paths. Need to permute to avoid all similar colours on top in graph
colours <- tibble(modrep = unique(future$modrep)) %>%
  mutate(col = sample(rainbow(1000)))
future <- future %>% left_join(colours, by = "modrep")
```

## Where is Melbourne?

\only<1>{\placefig{0.5}{1.3}{height=8cm,width=15cm}{melbourne-location-on-the-us-map}}
\only<2-4>{\placefig{0.5}{1.3}{height=8cm,width=15cm}{melbourne-location-on-the-australia-map}}
\begin{textblock}{12.5}(1.9,8.6)\fontsize{7}{8}\sf\url{ontheworldmap.com}\end{textblock}
\only<3-4>{\placefig{11.4}{1.5}{width=4.5cm}{coffee}}
\only<4>{\placefig{11.4}{4.5}{width=4.5cm}{degraves}}

## Australian monthly café turnover

```{r data, echo=FALSE, dependson='samples'}
p1 <- train %>%
  autoplot(turnover) +
  labs(
    x = "Month",
    y = "Turnover (A$million)",
    title = "Australian monthly café turnover"
  ) +
  guides(colour = FALSE, level = FALSE)
p1 +
  geom_line(
    data = filter(future, as.numeric(.rep) <= 5),
    aes(y = .sim, col = col, group = c(modrep)),
    alpha = 0
  )
```

\placefig{11.4}{1.5}{width=4.5cm}{coffee}
\placefig{11.4}{4.5}{width=4.5cm}{degraves}

## Forecasting using possible futures

```{r plots, echo=FALSE, dependson="data"}
p1 +
  geom_line(
    data = filter(future, as.numeric(.rep) <= 5),
    aes(y = .sim, col = col, group = c(modrep))
  ) +
  annotate("text", x=as.Date("2019-06-01"), y=3200, label="ETS futures")
```

\placefig{11.4}{1.5}{width=4.5cm}{coffee}
\placefig{11.4}{4.5}{width=4.5cm}{degraves}

## Forecasting using possible futures

```{r samples2, echo=FALSE, dependson='data'}
p1$data <- train %>% filter(year(date) >= 2015)
p1 <- p1 +
  ylim(min(p1$data$turnover), max(future$.sim))
p1 +
  geom_line(
    data = filter(future, as.numeric(.rep) <= 5),
    aes(y = .sim, col = col, group = c(modrep)),
  ) +
  annotate("text", x=as.Date("2019-06-01"), y=3200, label="ETS futures")
```

\placefig{11.4}{1.5}{width=4.5cm}{coffee}
\placefig{11.4}{4.5}{width=4.5cm}{degraves}

## Forecasting using possible futures

```{r samples2a, echo=FALSE, dependson='samples2'}
p1 +
  geom_line(
    data = filter(future),
    aes(y = .sim, col = col, group = c(modrep)),
  ) +
  annotate("text", x=as.Date("2019-06-01"), y=3200, label="ETS futures")
```

\placefig{11.4}{1.5}{width=4.5cm}{coffee}
\placefig{11.4}{4.5}{width=4.5cm}{degraves}


## Forecasting using possible futures

```{r samples3, echo=FALSE, dependson='samples2'}
p1 <- p1 +
  geom_line(
    data = future,
    aes(y = .sim, group = modrep),
    color = "gray", alpha = 0.2
  ) +
  annotate("text", x=as.Date("2019-06-01"), y=3200, label="ETS futures", col='gray')
p1 
```

\placefig{11.4}{1.5}{width=4.5cm}{coffee}
\placefig{11.4}{4.5}{width=4.5cm}{degraves}

## Forecasting using possible futures

```{r point, echo=FALSE, dependson='samples3'}
p1 +
  autolayer(fc, level = NULL, lwd = 1)
```

\begin{textblock}{4.2}(11.5,1.5)\fontsize{11}{13}\sf
\begin{block}{}
\textbf{Point forecasts:} means of the sample paths.
\end{block}
\end{textblock}

## Forecasting using possible futures

```{r interval, echo=FALSE, dependson='samples3'}
p1 +
  autolayer(fc, level = 80, lwd = 1)
```

\begin{textblock}{4.2}(11.5,1.5)\fontsize{11}{13}\sf
\begin{block}{}
\textbf{Point forecasts:} means of the sample paths.
\end{block}
\begin{block}{}
\textbf{Prediction intervals:} middle 80\% of the sample paths at each forecast horizon.
\end{block}
\end{textblock}

## Forecasting using possible futures

```{r quantile, echo=FALSE, dependson='samples3'}
p1 +
  autolayer(fc, level = 80, lwd = 1)
```

\begin{textblock}{4.2}(11.5,1.5)\fontsize{11}{13}\sf
\begin{block}{}
\textbf{Point forecasts:} means of the sample paths.
\end{block}
\begin{block}{}
\textbf{Prediction intervals:} middle 80\% of the sample paths at each forecast horizon.
\end{block}
\begin{block}{}
\textbf{Quantile forecasts:} Quantiles of the sample paths at each forecast horizon.
\end{block}
\end{textblock}


## Quantile forecasts

```{r quantiles, dependson='samples3'}
qf <- fit %>%
  generate(times = 1000, h = "1 year") %>%
  as_tibble() %>%
  group_by(date) %>%
  summarise(
    qs = quantile(.sim, seq(from = 0.1, to = 0.9, by = 0.1)), prob = seq(from = 0.1, to = 0.9, by = 0.1)
  )
p1 <- p1 +
  geom_line(
    data = qf,
    mapping = aes(x = date, y = qs, group = prob),
    colour = "blue"
  )
p1
```

\begin{textblock}{4.2}(11.5,1.5)\fontsize{11}{13}\sf
\begin{block}{}
\textbf{Blue:} Deciles for the ETS forecasts for the Australian monthly café turnover.
\end{block}
\end{textblock}

## Quantile forecasts

```{r quantiles3, dependson='quantiles'}
p1 +
  geom_line(aes(y = turnover), data = cafe %>% filter(year(date) >= 2018))
```

\begin{textblock}{4.2}(11.5,1.5)\fontsize{11}{13}\sf
\begin{block}{}
\textbf{Blue:} Deciles for the ETS forecasts for the Australian monthly café turnover. \textbf{Black:} Observed values.
\end{block}
\end{textblock}

## Evaluating quantile forecasts

\begin{textblock}{9.5}(0.2,1.2)
\begin{alertblock}{}\vspace*{-0.8cm}
\begin{align*}
f_{p,t} &= \text{quantile forecast with prob. $p$ at time $t$.}\\
y_{t} &= \text{observation at time $t$}
\end{align*}
\end{alertblock}\vspace*{-0.3cm}
\uncover<2->{\begin{block}{Quantile score}\vspace*{-0.6cm}
$$
  Q_{p,t} = \begin{cases}
  2(1 - p) \big|y_t - f_{p,t}\big|, & \text{if $y_{t} < f_{p,t}$}\\
  2p \big|y_{t} - f_{p,t}\big|, & \text{if $y_{t} \ge f_{p,t}$} \end{cases}
$$
\end{block}}
\end{textblock}
\begin{textblock}{15}(0.2,5.6)
\uncover<4->{
\begin{itemize}\itemsep=0cm\parskip=0cm
\item Low $Q_p$ is good
\item Multiplier of 2 often omitted, but useful for interpretation
\item $Q_p$ like absolute error (weighted to account for likely exceedance)
\item Average $Q_p$ = CRPS (Continuous Rank Probability Score)
\end{itemize}}
\end{textblock}
\begin{textblock}{6}(10,2)
\only<3->{\animategraphics[loop,autoplay]{10}{ensembles_NYCR_2020_files/figure-beamer/pinball-}{1}{100}}
\end{textblock}

```{r pinball, eval=FALSE, echo=FALSE, fig.show='animate', interval=1/10, message=FALSE, fig.height=3, fig.width=5, cache=FALSE}
# Turn eval=TRUE to recompute these graphs. They are loaded in the above animategraphics call.
prob <- seq(0.05, 0.95, by = 0.05)
df <- expand.grid(
  error = c(-10, 0, 10),
  p = c(prob, rev(head(prob, -1)[-1]))
) %>%
  mutate(
    state = rep(seq(length(p) / 3), rep(3, length(p) / 3)),
    qpt = 2 * p * error * (error > 0) - 2 * (1 - p) * error * (error < 0)
  )
labels <- df %>%
  select(p, state) %>%
  distinct() %>%
  mutate(label = paste0("p = ", sprintf("%.2f", p)))
df %>% ggplot(aes(x = error, y = qpt)) +
  geom_line(aes(group = state), colour = "red") +
  labs(
    x = latex2exp::TeX("Error: $y_t - f_{p,t}$"),
    y = latex2exp::TeX("Q_{p,t}")
  ) +
  geom_label(data = labels, aes(x = 0, y = 17, label = label)) +
  transition_states(state)
```
  
## Evaluating quantile forecasts
\fontsize{9}{10}\sf

\btwocol

```{r crps0, echo=TRUE}
cafe 
```

\etwocol

\vspace*{10cm}

## Evaluating quantile forecasts
\fontsize{9}{10}\sf

\btwocol

```{r crps1, echo=TRUE}
cafe %>%
  filter(year(date) <= 2018)
```

\etwocol

\vspace*{10cm}
## Evaluating quantile forecasts
\fontsize{9}{10}\sf

\btwocol

```{r crps2, echo=TRUE}
cafe %>%
  filter(year(date) <= 2018) %>%
  model(
    ETS = ETS(turnover),
    ARIMA = ARIMA(turnover ~ 
                  pdq(d=1) + PDQ(D=1))
  )
```

\etwocol

\vspace*{10cm}

## Evaluating quantile forecasts
\fontsize{9}{10}\sf

\btwocol

```{r crps3, echo=TRUE}
cafe %>%
  filter(year(date) <= 2018) %>%
  model(
    ETS = ETS(turnover),
    ARIMA = ARIMA(turnover ~ 
                  pdq(d=1) + PDQ(D=1))
  ) %>%
  forecast(h = "1 year")
```

\etwocol

\vspace*{10cm}

## Evaluating quantile forecasts
\fontsize{9}{10}\sf

\btwocol

```{r crps4, echo=TRUE}
cafe %>%
  filter(year(date) <= 2018) %>%
  model(
    ETS = ETS(turnover),
    ARIMA = ARIMA(turnover ~ 
                  pdq(d=1) + PDQ(D=1))
  ) %>%
  forecast(h = "1 year") %>%
  accuracy(
    data = cafe, 
    measures = list(crps=CRPS, rmse=RMSE)
  ) %>%
  arrange(crps)
```

\etwocol

\vspace*{10cm}

## Ensemble forecasting
\fontsize{11}{12}\sf

**Ensemble forecasting** involves combining the forecast distributions from multiple models. 

  * “All models are wrong, but some are useful” (George Box, 1976)
  * Allows diverse models to be included, while reducing impact of any specific model. 
  * Allows uncertainty of model selection to be incorporated.

```{r ensemble_samples, echo=FALSE, fig.height=2.6}
fit <- cafe %>%
  filter(year(date) <= 2018) %>%
  model(
    ETS = ETS(turnover),
    ARIMA = ARIMA(turnover ~ 
                  pdq(d=1) + PDQ(D=1))
  )
future <- fit %>%
  generate(times = 10, h = "1 year")
cafe %>%
  filter(year(date) >= 2014, year(date) <= 2018) %>%
  autoplot(turnover) +
  geom_line(data = future %>% mutate(modrep = paste0(.model, .rep)), aes(y = .sim, col = .model, group = c(modrep))) +
  labs(x = "Month", y = "Turnover (A$million)") +
  guides(colour = guide_legend("Model"))
```  

## Ensemble forecasting
\fontsize{9}{10}\sf

\btwocol

```{r ensemble1, echo=TRUE}
cafe %>%
  filter(year(date) <= 2018) %>%
  model(
    ETS = ETS(turnover),
    ARIMA = ARIMA(turnover ~ 
                  pdq(d=1) + PDQ(D=1))
  ) %>%
  forecast(h = "1 years")
```

\etwocol

\vspace*{10cm}

## Ensemble forecasting
\fontsize{9}{10}\sf

\btwocol

```{r ensemble2, echo=TRUE, dependson='ensemble1a'}
cafe %>%
  filter(year(date) <= 2018) %>%
  model(
    ETS = ETS(turnover),
    ARIMA = ARIMA(turnover ~ 
                  pdq(d=1) + PDQ(D=1))
  ) %>%
  forecast(h = "1 year") %>%
  summarise(
    turnover = dist_mixture(
      turnover[1], 
      turnover[2], 
      weights = c(0.5, 0.5)
    )
  )
```

\etwocol

\vspace*{10cm}

## Ensemble forecasting
\fontsize{9}{10}\sf

\btwocol

```{r ensemble3, echo=TRUE, dependson='ensemble1a'}
cafe %>%
  filter(year(date) <= 2018) %>%
  model(
    ETS = ETS(turnover),
    ARIMA = ARIMA(turnover ~ 
                  pdq(d=1) + PDQ(D=1))
  ) %>%
  forecast(h = "1 year") %>%
  summarise(
    turnover = dist_mixture(
      turnover[1], 
      turnover[2], 
      weights = c(0.5, 0.5)
    )
  ) %>%
  as_fable(response = "turnover", 
           distribution = turnover)
```

\etwocol

\vspace*{10cm}

## Ensemble forecasting
\fontsize{9}{10}\sf

\btwocol

```{r ensemble4, echo=TRUE, dependson='ensemble2a'}
cafe %>%
  filter(year(date) <= 2018) %>%
  model(
    ETS = ETS(turnover),
    ARIMA = ARIMA(turnover ~ 
                  pdq(d=1) + PDQ(D=1))
  ) %>%
  forecast(h = "1 year") %>%
  summarise(
    turnover = dist_mixture(
      turnover[1], 
      turnover[2], 
      weights = c(0.5, 0.5)
    )
  ) %>%
  as_fable(response = "turnover", 
           distribution = turnover) %>%
  accuracy(
    data = cafe, 
    measures = list(crps=CRPS, rmse=RMSE)
  )
```

\pause\color{Orange}\textbf{Comparison:}

```{r crps_comparison, ref.label="crps4", echo=FALSE}
```

\etwocol

\vspace*{10cm}

## Combination forecasting
\fontsize{13}{15}\sf

**Combination forecasting**: weighted averages of forecasts from multiple models. 

  * Often a simple average is used. 
  * Reduces uncertainty associated with selecting a particular model.
  * Combination forecasting usually improves point forecast accuracy.
  * Mean forecast identical to that from corresponding weighted ensemble.
  * Quantile forecasts need to account for correlations between forecast errors from component models.

## Combination forecasting
\fontsize{9}{10}\sf

\btwocol

```{r combinations1, echo=TRUE}
cafe %>%
  filter(year(date) <= 2018) %>%
  model(
    ETS = ETS(turnover),
    ARIMA = ARIMA(turnover ~ 
                  pdq(d=1) + PDQ(D=1))
  ) 
```

\etwocol

\vspace*{10cm}

## Combination forecasting
\fontsize{9}{10}\sf

\btwocol

```{r combinations2, echo=TRUE}
cafe %>%
  filter(year(date) <= 2018) %>%
  model(
    ETS = ETS(turnover),
    ARIMA = ARIMA(turnover ~ 
                  pdq(d=1) + PDQ(D=1))
  ) %>%
  mutate(COMB = (ETS + ARIMA)/2)
```

\etwocol

\vspace*{10cm}

## Combination forecasting
\fontsize{9}{10}\sf

\btwocol

```{r combinations3, echo=TRUE}
cafe %>%
  filter(year(date) <= 2018) %>%
  model(
    ETS = ETS(turnover),
    ARIMA = ARIMA(turnover ~ 
                  pdq(d=1) + PDQ(D=1))
  ) %>%
  mutate(COMB = (ETS + ARIMA)/2) %>%
  forecast(h = "1 year") 
```

\etwocol

\vspace*{10cm}

## Combination forecasting
\fontsize{9}{10}\sf

\btwocol

```{r combinations4, echo=TRUE}
cafe %>%
  filter(year(date) <= 2018) %>%
  model(
    ETS = ETS(turnover),
    ARIMA = ARIMA(turnover ~ 
                  pdq(d=1) + PDQ(D=1))
  ) %>%
  mutate(COMB = (ETS + ARIMA)/2) %>%
  forecast(h = "1 year") %>%
  accuracy(
    data = cafe, 
    measures = list(crps=CRPS, rmse=RMSE)
  ) %>%
  arrange(crps)
```

\etwocol

\vspace*{10cm}


## fable packages
\fontsize{15}{17}\sf

\placefig{2}{1.5}{height=5cm, width=14cm, keepaspectratio=true}{fable.png}
\begin{textblock}{4.3}(2,6.5)\begin{block}{}\centering fable.tidyverts.org\end{block}\end{textblock}

\placefig{8.7}{1.5}{height=5cm, width=14cm, keepaspectratio=true}{mitch2.jpg}
\begin{textblock}{4.7}(8.8,6.5)\begin{block}{}\centering Mitchell O'Hara-Wild\rlap{\phantom{g}}\end{block}\end{textblock}

\only<2>{\begin{textblock}{6.3}(9.3,7.8)\begin{alertblock}{}robjhyndman.com/nycr2020\end{alertblock}\end{textblock}}



