---
title: "Ensemble forecasts with fable"
author: Rob J Hyndman
date: "NYR Conference: 14 August 2020"
fontsize: 14pt
titlefontsize: 32pt
classoption: aspectratio=169
toc: true
output:
  binb::monash:
    fig_height: 4.33
    fig_width: 7
    colortheme: monashwhite
    keep_tex: yes
    includes:
      in_header: preamble.tex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  cache = TRUE,
  dev.args = list(bg = grey(0.9), pointsize = 11)
)
options(width=45)
library(fpp3)
library(distributional)
library(gganimate)
library(stringr)
library(ggdist)
set.seed(2020 - 08 - 10)

if (file.exists("cafe.rds")) {
  cafe <- readRDS("cafe.rds")
} else {
  cafe <- readabs::read_abs(cat_no="8501.0", tables=11) %>%
    filter(str_detect(series, "takeaway")) %>%
    mutate(
      state = str_extract(series, "^Turnover ;  ([A-Za-z\\s]*)*"),
      state = str_trim(str_remove(state, "Turnover ;  ")),
      state = recode(state,
        `Australian Capital Territory` = "ACT",
        `New South Wales` = "NSW",
        `Northern Territory` = "NT",
        Queensland = "QLD",
        `South Australia` = "SA",
        Tasmania = "TAS",
        Victoria = "VIC",
        `Western Australia` = "WA"
      ),
      date = yearmonth(date)
    ) %>%
    select(date, state, value) %>%
    filter(state != "Total") %>%
    rename(turnover = value) %>%
    filter(
      date >= yearmonth("2006 Jan"),
      date <= yearmonth("2019 Dec")
    ) %>%
    as_tsibble(index=date, key=state)
  saveRDS(cafe, "cafe.rds")
}
auscafe <- cafe %>%
  summarise(turnover = sum(turnover))
```

```{r samples, echo=FALSE}
# Training data
train <- auscafe %>%
  filter(year(date) <= 2018)
# Fit ETS model
fit <- train %>%
  model(ETS = ETS(turnover))
# Forecasts
fc <- fit %>%
  forecast(h = "1 year")
# Future sample paths
future <- fit %>%
  generate(times = 1000, h = "1 year") %>%
  as_tibble() %>%
  mutate(modrep = paste0(.model, .rep))
# Colours for sample paths. Need to permute to avoid all similar colours on top in graph
colours <- tibble(modrep = unique(future$modrep)) %>%
  mutate(col = sample(rainbow(1000)))
future <- future %>% left_join(colours, by = "modrep")
```

# Quantile forecasting

## Where is Melbourne?

\only<1>{\placefig{0.5}{1.3}{height=8cm,width=15cm}{melbourne-location-on-the-us-map}}
\only<2-4>{\placefig{0.5}{1.3}{height=8cm,width=15cm}{melbourne-location-on-the-australia-map}}
\begin{textblock}{12.5}(1.9,8.6)\fontsize{7}{8}\sf\url{ontheworldmap.com}\end{textblock}
\only<3-4>{\placefig{11.4}{1.5}{width=4.5cm}{coffee}}
\only<4>{\placefig{11.4}{4.5}{width=4.5cm}{degraves}}

## Australian monthly café turnover

```{r data, echo=FALSE, dependson='samples'}
p1 <- train %>%
  autoplot(turnover) +
  labs(
    x = "Month",
    y = "Turnover (A$million)",
    title = "Australian monthly café turnover"
  ) +
  guides(colour = FALSE, level = FALSE)
p1 +
  geom_line(
    data = filter(future, as.numeric(.rep) <= 5),
    aes(y = .sim, col = col, group = c(modrep)),
    alpha = 0
  )
```

\placefig{11.4}{1.5}{width=4.5cm}{coffee}
\placefig{11.4}{4.5}{width=4.5cm}{degraves}

\only<2>{\begin{textblock}{5.7}(2.2,1.9)\begin{block}{}\fontsize{9}{11}\sf
\texttt{train \%>\%}\\
\texttt{  autoplot(turnover)}
\end{block}\end{textblock}}

\vspace*{10cm}

## Australian monthly café turnover

```{r plots2, echo=FALSE, dependson="data"}
p1 +
  geom_line(
    data = filter(future, as.numeric(.rep) <= 5),
    aes(y = .sim, col = col, group = c(modrep))
  ) +
  annotate("text", x=as.Date("2019-06-01"), y=3200, label="ETS futures")
```

\placefig{11.4}{1.5}{width=4.5cm}{coffee}
\placefig{11.4}{4.5}{width=4.5cm}{degraves}

\begin{textblock}{5.7}(2.2,1.9)\begin{block}{}\fontsize{9}{11}\sf
\texttt{train \%>\%}\\
\texttt{  model(ETS = ETS(turnover))}\\
\texttt{  generate(times=5, h="1 year") \%>\%}\\
\texttt{  autoplot() + autolayer(train)}\end{block}\end{textblock}

\vspace*{10cm}

## Australian monthly café turnover

```{r samples2, echo=FALSE, dependson='data'}
p1$data <- train %>% filter(year(date) >= 2015)
p1 <- p1 +
  ylim(min(p1$data$turnover), max(future$.sim))
p1 +
  geom_line(
    data = filter(future, as.numeric(.rep) <= 5),
    aes(y = .sim, col = col, group = c(modrep)),
  ) +
  annotate("text", x=as.Date("2019-06-01"), y=3200, label="ETS futures")
```

\placefig{11.4}{1.5}{width=4.5cm}{coffee}
\placefig{11.4}{4.5}{width=4.5cm}{degraves}

## Australian monthly café turnover

```{r samples2a, echo=FALSE, dependson='samples2'}
p1 +
  geom_line(
    data = filter(future),
    aes(y = .sim, col = col, group = c(modrep)),
  ) +
  annotate("text", x=as.Date("2019-06-01"), y=3200, label="ETS futures")
```

\placefig{11.4}{1.5}{width=4.5cm}{coffee}
\placefig{11.4}{4.5}{width=4.5cm}{degraves}

## Australian monthly café turnover

```{r samples3, echo=FALSE, dependson='samples2'}
p1 <- p1 +
  geom_line(
    data = future,
    aes(y = .sim, group = modrep),
    color = "gray", alpha = 0.2
  ) +
  annotate("text", x=as.Date("2019-06-01"), y=3200, label="ETS futures", col='gray')
p1
```

\placefig{11.4}{1.5}{width=4.5cm}{coffee}
\placefig{11.4}{4.5}{width=4.5cm}{degraves}

## Forecasting using possible futures

```{r point, echo=FALSE, dependson='samples3'}
p1 +
  autolayer(fc, level = NULL, lwd = 1)
```

\begin{textblock}{4.2}(11.5,1.5)\fontsize{11}{13}\sf
\begin{block}{}
\textbf{Point forecasts:} means of the sample paths.
\end{block}
\end{textblock}

## Forecasting using possible futures

```{r interval, echo=FALSE, dependson='samples3'}
p1 +
  autolayer(fc, level = 80, lwd = 1)
```

\begin{textblock}{4.2}(11.5,1.5)\fontsize{11}{13}\sf
\begin{block}{}
\textbf{Point forecasts:} means of the sample paths.
\end{block}
\begin{block}{}
\textbf{Prediction intervals:} middle 80\% of the sample paths at each forecast horizon.
\end{block}
\end{textblock}

## Forecasting using possible futures

```{r quantile, echo=FALSE, dependson='samples3'}
p1 +
  autolayer(fc, level = 80, lwd = 1)
```

\begin{textblock}{4.2}(11.5,1.5)\fontsize{11}{13}\sf
\begin{block}{}
\textbf{Point forecasts:} means of the sample paths.
\end{block}
\begin{block}{}
\textbf{Prediction intervals:} middle 80\% of the sample paths at each forecast horizon.
\end{block}
\begin{block}{}
\textbf{Quantile forecasts:} Quantiles of the sample paths at each forecast horizon.
\end{block}
\end{textblock}


## Quantile forecasts

```{r quantiles, dependson='samples3'}
qf <- fit %>%
  generate(times = 1000, h = "1 year") %>%
  as_tibble() %>%
  group_by(date) %>%
  summarise(
    qs = quantile(.sim, seq(from = 0.1, to = 0.9, by = 0.1)), prob = seq(from = 0.1, to = 0.9, by = 0.1)
  )
p1 <- p1 +
  geom_line(
    data = qf,
    mapping = aes(x = date, y = qs, group = prob),
    colour = "blue"
  )
p1
```

\begin{textblock}{4.2}(11.5,1.5)\fontsize{11}{13}\sf
\begin{block}{}
\textbf{Blue:} Deciles for the ETS forecasts for the Australian monthly café turnover.
\end{block}
\end{textblock}

## Quantile forecasts

```{r quantiles3, dependson='quantiles'}
p1 +
  geom_line(aes(y = turnover), data = auscafe %>% filter(year(date) >= 2018))
```

\begin{textblock}{4.2}(11.5,1.5)\fontsize{11}{13}\sf
\begin{block}{}
\textbf{Blue:} Deciles for the ETS forecasts for the Australian monthly café turnover. \textbf{Black:} Observed values.
\end{block}
\end{textblock}

## Evaluating quantile forecasts

\begin{textblock}{9.5}(0.2,1.2)
\begin{alertblock}{}\vspace*{-0.2cm}
\begin{align*}
f_{p,t} &= \text{quantile forecast with prob. $p$ at time $t$.}\\
y_{t} &= \text{observation at time $t$}
\end{align*}
\end{alertblock}\vspace*{-0.3cm}
\uncover<2->{\begin{block}{Quantile score}\vspace*{-0.2cm}
$$
  Q_{p,t} = \begin{cases}
  2(1 - p) \big|y_t - f_{p,t}\big|, & \text{if $y_{t} < f_{p,t}$}\\
  2p \big|y_{t} - f_{p,t}\big|, & \text{if $y_{t} \ge f_{p,t}$} \end{cases}
$$
\end{block}}
\end{textblock}
\begin{textblock}{15}(0.2,5.6)
\uncover<4->{
\begin{itemize}\itemsep=0cm\parskip=0cm
\item Low $Q_{p,t}$ is good
\item Multiplier of 2 often omitted, but useful for interpretation
\item $Q_{p,t}$ like absolute error (weighted to account for likely exceedance)
\item Average $Q_{p,t}$ over $p$ = CRPS (Continuous Rank Probability Score)
\end{itemize}}
\end{textblock}
\begin{textblock}{6}(10,2)
\only<3->{\animategraphics[loop,autoplay]{10}{ensembles_NYCR_2020_files/figure-beamer/pinball-}{1}{100}}
\end{textblock}

```{r pinball, eval=FALSE, echo=FALSE, fig.show='animate', interval=1/10, message=FALSE, fig.height=3, fig.width=5, cache=FALSE}
# Turn eval=TRUE to recompute these graphs. They are loaded in the above animategraphics call.
prob <- seq(0.05, 0.95, by = 0.05)
df <- expand.grid(
  error = c(-10, 0, 10),
  p = c(prob, rev(head(prob, -1)[-1]))
) %>%
  mutate(
    state = rep(seq(length(p) / 3), rep(3, length(p) / 3)),
    qpt = 2 * p * error * (error > 0) - 2 * (1 - p) * error * (error < 0)
  )
labels <- df %>%
  select(p, state) %>%
  distinct() %>%
  mutate(label = paste0("p = ", sprintf("%.2f", p)))
df %>% ggplot(aes(x = error, y = qpt)) +
  geom_line(aes(group = state), colour = "red") +
  labs(
    x = latex2exp::TeX("Error: $y_t - f_{p,t}$"),
    y = latex2exp::TeX("Q_{p,t}")
  ) +
  geom_label(data = labels, aes(x = 0, y = 17, label = label)) +
  transition_states(state)
```


## Let's do some coding
\fontsize{15}{17}\sf

\begin{textblock}{4.3}(11,.1)\begin{alertblock}{}\centering tidyverts.org\end{alertblock}\end{textblock}

\placefig{2}{1.5}{height=3.5cm, width=14cm, keepaspectratio=true}{tsibble.png}
\placefig{2}{5.3}{height=3.5cm, width=14cm, keepaspectratio=true}{fable.png}

\placefig{6.7}{1.5}{height=4.2cm, width=14cm, keepaspectratio=true}{earowang.jpg}
\begin{textblock}{4.7}(10.8,1.5)\begin{block}{}\centering Earo Wang\rlap{\phantom{g}}\end{block}\end{textblock}

\placefig{6.7}{5.3}{height=3.5cm, width=14cm, keepaspectratio=true}{mitch2.jpg}
\begin{textblock}{4.7}(10.8,5.3)\begin{block}{}\centering Mitchell O'Hara-Wild\rlap{\phantom{g}}\end{block}\end{textblock}

## Evaluating quantile forecasts
\fontsize{9}{10}\sf

\btwocol

```{r crps0, echo=TRUE}
auscafe
```

\etwocol

\vspace*{10cm}

## Evaluating quantile forecasts
\fontsize{9}{10}\sf

\btwocol

```{r crps1, echo=TRUE}
auscafe %>%
  filter(year(date) <= 2018)
```

\etwocol

\vspace*{10cm}
## Evaluating quantile forecasts
\fontsize{9}{10}\sf

\btwocol

```{r crps2, echo=TRUE}
auscafe %>%
  filter(year(date) <= 2018) %>%
  model(
    ETS = ETS(turnover),
    ARIMA = ARIMA(turnover ~
                  pdq(d=1) + PDQ(D=1))
  )
```

\etwocol

\vspace*{10cm}

## Evaluating quantile forecasts
\fontsize{9}{10}\sf

\btwocol

```{r crps3, echo=TRUE}
auscafe %>%
  filter(year(date) <= 2018) %>%
  model(
    ETS = ETS(turnover),
    ARIMA = ARIMA(turnover ~
                  pdq(d=1) + PDQ(D=1))
  ) %>%
  forecast(h = "1 year")
```

\etwocol

\vspace*{10cm}

## Evaluating quantile forecasts
\fontsize{9}{10}\sf

\btwocol

```{r crps4, echo=TRUE}
auscafe %>%
  filter(year(date) <= 2018) %>%
  model(
    ETS = ETS(turnover),
    ARIMA = ARIMA(turnover ~
                  pdq(d=1) + PDQ(D=1))
  ) %>%
  forecast(h = "1 year") %>%
  accuracy(data = auscafe,
    measures = list(crps=CRPS, rmse=RMSE)
  ) %>%
  arrange(crps)
```

\etwocol

\vspace*{10cm}

# Ensemble forecasting

## Ensemble forecasting
\fontsize{11}{12}\sf

\alert{\textbf{Ensemble forecasting}}: **mix the forecast distributions from multiple models.**

  * “All models are wrong, but some are useful” (George Box, 1976)
  * Allows diverse models to be included, while reducing impact of any specific model.
  * Allows uncertainty of model selection to be incorporated.

```{r ensemble_samples, echo=FALSE, fig.height=2.6}
fit <- auscafe %>%
  filter(year(date) <= 2018) %>%
  model(
    ETS = ETS(turnover),
    ARIMA = ARIMA(turnover ~
                  pdq(d=1) + PDQ(D=1))
  )
future <- fit %>%
  generate(times = 10, h = "1 year")
auscafe %>%
  filter(year(date) >= 2014, year(date) <= 2018) %>%
  autoplot(turnover) +
  geom_line(data = future %>% mutate(modrep = paste0(.model, .rep)), aes(y = .sim, col = .model, group = c(modrep))) +
  labs(x = "Month", y = "Turnover (A$million)") +
  guides(colour = guide_legend("Model")) 
```

## Ensemble forecasting
\fontsize{9}{10}\sf

\btwocol

```{r ensemble1, echo=TRUE}
auscafe %>%
  filter(year(date) <= 2018) %>%
  model(ETS = ETS(turnover),
        ARIMA = ARIMA(turnover ~
                    pdq(d=1) + PDQ(D=1))
  ) %>%
  forecast(h = "1 year")
```

\etwocol

\vspace*{10cm}

## Ensemble forecasting
\fontsize{9}{10}\sf

\btwocol

```{r ensemble2, echo=TRUE, dependson='ensemble1a'}
auscafe %>%
  filter(year(date) <= 2018) %>%
  model(ETS = ETS(turnover),
        ARIMA = ARIMA(turnover ~
                    pdq(d=1) + PDQ(D=1))
  ) %>%
  forecast(h = "1 year") %>%
  summarise(
    turnover = dist_mixture(
                turnover[1], turnover[2],
                weights=c(0.5,0.5))
  ) %>%
  mutate(.model = "ENSEMBLE") 
```

\etwocol

\vspace*{10cm}

## Ensemble forecasting
\fontsize{9}{10}\sf

\btwocol

```{r ensemble4, echo=TRUE, dependson='ensemble2a'}
auscafe %>%
  filter(year(date) <= 2018) %>%
  model(ETS = ETS(turnover),
        ARIMA = ARIMA(turnover ~
                    pdq(d=1) + PDQ(D=1))
  ) %>%
  forecast(h = "1 year") %>%
  summarise(
    turnover = dist_mixture(
                turnover[1], turnover[2],
                weights=c(0.5,0.5))
  ) %>%
  mutate(.model = "ENSEMBLE") %>%
  accuracy(
    data = auscafe,
    measures = list(crps=CRPS, rmse=RMSE)
  )
```

\pause\color{Orange}\textbf{Comparison:}

```{r crps_comparison, ref.label="crps4", echo=FALSE}
```

\vspace*{10cm}

\etwocol

\vspace*{10cm}

# Combination forecasting

## Combination forecasting
\fontsize{13}{15}\sf

\alert{\textbf{Combination forecasting}}: **take weighted average of forecasts from multiple models.**

  * Often a simple average is used.
  * Reduces uncertainty associated with selecting a particular model.
  * Combination forecasting usually improves point forecast accuracy.
  * Mean forecast identical to that from corresponding weighted ensemble.
  * Quantile forecasts need to account for correlations between forecast errors from component models.

## Combination forecasting
\fontsize{9}{10}\sf

\btwocol

```{r combinations1, echo=TRUE}
auscafe %>%
  filter(year(date) <= 2018) %>%
  model(
    ETS = ETS(turnover),
    ARIMA = ARIMA(turnover ~
                  pdq(d=1) + PDQ(D=1))
  )
```

\etwocol

\vspace*{10cm}

## Combination forecasting
\fontsize{9}{10}\sf

\btwocol

```{r combinations2, echo=TRUE}
auscafe %>%
  filter(year(date) <= 2018) %>%
  model(
    ETS = ETS(turnover),
    ARIMA = ARIMA(turnover ~
                  pdq(d=1) + PDQ(D=1))
  ) %>%
  mutate(COMB = (ETS + ARIMA)/2)
```

\etwocol

\vspace*{10cm}

## Combination forecasting
\fontsize{9}{10}\sf

\btwocol

```{r combinations3, echo=TRUE}
auscafe %>%
  filter(year(date) <= 2018) %>%
  model(
    ETS = ETS(turnover),
    ARIMA = ARIMA(turnover ~
                  pdq(d=1) + PDQ(D=1))
  ) %>%
  mutate(COMB = (ETS + ARIMA)/2) %>%
  forecast(h = "1 year")
```

\etwocol

\vspace*{10cm}

## Combination forecasting
\fontsize{9}{10}\sf

\btwocol

```{r combinations4, echo=TRUE}
auscafe %>%
  filter(year(date) <= 2018) %>%
  model(
    ETS = ETS(turnover),
    ARIMA = ARIMA(turnover ~
                  pdq(d=1) + PDQ(D=1))
  ) %>%
  mutate(COMB = (ETS + ARIMA)/2) %>%
  forecast(h = "1 year") %>%
  accuracy(
    data = auscafe,
    measures = list(crps=CRPS, rmse=RMSE)
  ) %>%
  arrange(crps)
```

\pause\color{Orange}\textbf{Comparison:}

```{r crps_comparison2, ref.label="ensemble4", echo=FALSE}
```

\vspace*{10cm}

\etwocol

\vspace*{10cm}

## Combination vs ensemble forecasting
\fontsize{9}{10}\sf

```{r comparison1, eval=TRUE}
train <- auscafe %>%
  filter(year(date) <= 2018)
fc <- train %>%
  model(
    ETS = ETS(turnover),
    ARIMA = ARIMA(turnover ~
                  pdq(d=1) + PDQ(D=1))
  ) %>%
  mutate(Combination = (ETS + ARIMA)/2) %>%
  forecast(h = "1 year")
ensemble <- fc %>%
  filter(.model %in% c("ETS", "ARIMA")) %>%
  summarise(
    turnover = dist_mixture(
                turnover[1], turnover[2],
                weights = c(0.5, 0.5))
  ) %>%
  mutate(.model = "Ensemble") %>%
  as_tibble() %>%
  select(date,.model,turnover)
combination  <- fc %>%
  filter(.model=="Combination") %>%
  as_tibble() %>%
  select(date,.model,turnover)
fc2 <- bind_rows(ensemble, combination) %>%
  mutate(.model = factor(.model, levels=c("Combination","Ensemble"))) %>%
  as_fable(index=date, key=.model, distribution=turnover, response="turnover") 
fc2 %>% autoplot(train %>% filter(year(date) >= 2017))
```

## Combination vs ensemble forecasting
\fontsize{9}{10}\sf

```{r comparison2, eval=TRUE, dependson='samples'}
fc2 %>% autoplot(train %>% filter(year(date) >= 2017)) +
  autolayer(filter(fc2, .model=="Combination"), color='red') 
```

## Combination vs ensemble forecasting
\fontsize{9}{10}\sf

```{r comparison3}
fc_combined <- tibble(
  .model = c("Combination", "Mixture"),
  dist = c((dist_normal(3700, 80) + dist_normal(3900, 120))/2,
           dist_mixture(dist_normal(3700, 80), dist_normal(3900, 120), weights = c(0.5, 0.5)))
)
fc_base <- tidyr::expand_grid(
    .model = c("Combination", "Mixture"),
    dist = c(dist_normal(3700, 80), dist_normal(3900, 120)),
  ) %>% 
  mutate(.base = rep(c("ETS", "ARIMA"), 2))

ggplot() + 
  stat_dist_slab(aes(dist = dist, y = ""), data = fc_combined) +
  stat_dist_slab(aes(dist = dist, y = "", colour = .base), size = 0.3, fill = NA, data = fc_base) + 
  geom_vline(aes(xintercept = mu, linetype = "Mean"), mutate(fc_combined, mu = mean(dist))) +
  geom_vline(aes(xintercept = median, linetype = "Median"), mutate(fc_combined, median = median(dist))) +
  coord_cartesian(expand = FALSE) +
  facet_grid(vars(.model), switch = "y") +
  theme(legend.position = "bottom") +
  labs(y = NULL, x = NULL, colour = "Model", linetype = "Forecast") +
  scale_colour_brewer(palette = "Dark2")   
```

\only<2->{\begin{textblock}{4.3}(11.4,2)
\begin{block}{}
\begin{itemize}
\item Combinations involve averaging the distributions, taking account of correlations between distributions.
\item Ensembles involve mixing the distributions, ignoring correlations between distributions.
\item The means are the same, but other characteristics are different.
\end{itemize}
\end{block}
\end{textblock}}


# Forecasting many series

## Forecasting many series
\fontsize{9}{10}\sf

\btwocol

```{r states1, echo=TRUE}
cafe
```

\etwocol

\vspace*{10cm}

## Forecasting many series
\fontsize{9}{10}\sf

```{r states_plot2, include=FALSE}
pdf(file = "figs/state_plot.pdf", width=22/2.54, height=10/2.54)
p <- cafe %>%
  autoplot(turnover) +
  labs(
    x = "Month",
    y = "Turnover (A$million)",
    title = "Australian monthly café turnover"
  )
print(p)
crop::dev.off.crop()
```

\btwocol

```{r states_plot, echo=TRUE, eval=FALSE}
cafe %>% autoplot(turnover)
```

\etwocol

\placefig{1}{2.4}{width=15cm}{state_plot}

\vspace*{10cm}

## Forecasting many series
\fontsize{9}{10}\sf

\btwocol

```{r states2, echo=TRUE}
cafe %>%
  filter(year(date) <= 2018)
```

\etwocol

\vspace*{10cm}
## Forecasting many series
\fontsize{9}{10}\sf

\btwocol

```{r states3, echo=TRUE}
cafe %>%
  filter(year(date) <= 2018) %>%
  model(
    ETS = ETS(turnover),
    ARIMA = ARIMA(turnover ~
                  pdq(d=1) + PDQ(D=1)),
    SNAIVE = SNAIVE(turnover)
  ) %>%
  mutate(
    COMB = (ETS+ARIMA)/2
  )
```

\etwocol

\vspace*{10cm}

## Forecasting many series
\fontsize{9}{10}\sf

\btwocol

```{r states4, echo=TRUE}
cafe %>%
  filter(year(date) <= 2018) %>%
  model(
    ETS = ETS(turnover),
    ARIMA = ARIMA(turnover ~
                  pdq(d=1) + PDQ(D=1)),
    SNAIVE = SNAIVE(turnover)
  ) %>%
  mutate(
    COMB = (ETS+ARIMA)/2
  ) %>%
  forecast(h = "1 year")
```

\etwocol

\vspace*{10cm}

## Forecasting many series
\fontsize{9}{10}\sf

\btwocol

```{r states5, echo=TRUE}
cafe %>%
  filter(year(date) <= 2018) %>%
  model(
    ETS = ETS(turnover),
    ARIMA = ARIMA(turnover ~
                  pdq(d=1) + PDQ(D=1)),
    SNAIVE = SNAIVE(turnover)
  ) %>%
  mutate(
    COMB = (ETS+ARIMA)/2
  ) %>%
  forecast(h = "1 year") %>%
  accuracy(data = cafe,
    measures = list(crps=CRPS, rmse=RMSE)
  )
```

\etwocol

\vspace*{10cm}


## Forecasting many series
\fontsize{9}{10}\sf

\btwocol

```{r states6, echo=TRUE}
cafe %>%
  filter(year(date) <= 2018) %>%
  model(
    ETS = ETS(turnover),
    ARIMA = ARIMA(turnover ~
                  pdq(d=1) + PDQ(D=1)),
    SNAIVE = SNAIVE(turnover)
  ) %>%
  mutate(
    COMB = (ETS+ARIMA)/2
  ) %>%
  forecast(h = "1 year") %>%
  accuracy(data = cafe,
    measures = list(ss=skill_score(CRPS))
  ) 
```

\etwocol

\vspace*{10cm}

\only<2>{\begin{textblock}{6}(9,7.2)\begin{block}{}\fontsize{14}{16}\sf
Skill score is relative to seasonal naive forecasts
\end{block}\end{textblock}}


## Forecasting many series
\fontsize{9}{10}\sf

\btwocol

```{r states8, echo=TRUE}
cafe %>%
  filter(year(date) <= 2018) %>%
  model(
    ETS = ETS(turnover),
    ARIMA = ARIMA(turnover ~
                  pdq(d=1) + PDQ(D=1)),
    SNAIVE = SNAIVE(turnover)
  ) %>%
  mutate(
    COMB = (ETS+ARIMA)/2
  ) %>%
  forecast(h = "1 year") %>%
  accuracy(data = cafe,
    measures = list(ss=skill_score(CRPS))
  ) %>%
  group_by(.model) %>%
  summarise(sspc = mean(ss) * 100)
```

\etwocol

\vspace*{10cm}

\begin{textblock}{6}(9,7.2)\begin{block}{}\fontsize{14}{16}\sf
Skill score is relative to seasonal naive forecasts
\end{block}\end{textblock}



## More information
\fontsize{15}{20}\sf

 * Slides and code: **robjhyndman.com/nycr2020**
 * Packages: **tidyverts.org**
 * Forecasting textbook using fable package: **OTexts.com/fpp3**

\begin{textblock}{7}(8.6,4.9)
\begin{alertblock}{Find me at ...}
\href{https://twitter.com/robjhyndman}{\faicon{twitter} @robjhyndman}

\href{https://github.com/robjhyndman}{\faicon{github}  @robjhyndman}

\href{https://robjhyndman.com}{\faicon{home} robjhyndman.com}

\href{mailto:rob.hyndman@monash.edu}{\faicon{envelope}  rob.hyndman@monash.edu}
\end{alertblock}
\end{textblock}
\vspace*{10cm}

